COG-ED Manuscript

### 2022-01-28 06_Paper/COG-ED/Manuscript.Rmd
added comment on figure 1

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
```
*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

>>>>

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE} 
# comment Christoph: Evtl. lieber mit fig.cap = "..." im Chunk arbeiten? Dann wäre das auf jeden fall immer an die Figure attached
include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
```
*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
